\documentclass[11pt,a4paper]{article}

\usepackage[top=1in,bottom=0.4in,left=0.75in,right=0.75in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{ragged2e}
\usepackage{fontawesome5}
\usepackage{graphicx}
\usepackage{tikz}

\pagenumbering{gobble}

\newcommand{\sectionhr}[1]{
  \section*{#1}
  \noindent\hrule\vspace{0.4em}
}

\titlespacing*{\section}{0pt}{0.5em}{0.3em}
\setlist[itemize]{leftmargin=*, before=\vspace{-0.3em}, after=\vspace{-0.3em}, itemsep=0.2em, parsep=0em}

\newcommand{\cventry}[5]{
  \noindent\textbf{#1} — \textit{#2} \hfill \textit{#3 — #4} 
  #5
}

\newcommand{\projectentry}[4]{
  \noindent\textbf{#1} \quad\textbar\quad \textit{#2}\newline
  \vspace{-1.25em}
  #3
  #4
}

\usepackage{charter}

\begin{document}

\vspace*{-2.5cm}

% ------------------------------------
% HEADER
% ------------------------------------
\begin{center}
{\huge \textbf{Elie-Joe Farah}}\\[0.3em]

\small
\faEnvelope\ \href{mailto:eliejoefarah@gmail.com}{eliejoefarah@gmail.com} \hspace{1em}
\faPhoneSquare\ +32 (0)498 21 71 68 \hspace{1em}
\faMapMarker\ Brussels, Belgium \hspace{1em}
\faLinkedin\ \href{https://www.linkedin.com/in/elie-joe-farah-7b1586230/}{linkedin}
\end{center}

% ------------------------------------
% EDUCATION
% ------------------------------------
\sectionhr{Education}
\noindent\textbf{BE in Computer Engineering, Dean's Honor List} — Lebanese American University \hfill \textit{2021--2025}\\
\noindent\textbf{Master en Ingénieur Civil en Informatique} — Université Libre de Bruxelles  \hfill \textit{2025--present}

% ------------------------------------
% EXPERIENCE
% ------------------------------------
\sectionhr{Professional Experience}

\cventry{QA Intern}{FOO}{Beirut}{Jun 2025 -- Jul 2025}{
  \begin{itemize}
    \item Executed 2,500+ mobile/web test cases, contributing to early detection of regressions in production-facing applications.
    \item Reported 25+ critical bugs via Jira, improving workflow clarity and test coverage.
    \item Coordinated with developers to refine documentation and accelerate issue resolution.
  \end{itemize}
}

\cventry{Software Development and QA Intern}{ITG - ITB}{Beirut}{Jun 2024 -- Aug 2024}{
  \begin{itemize}
    \item Built a PHP Laravel backend demo with REST-style API structuring and authentication workflows.
    \item Performed data-driven testing, identifying 20+ major issues and improving system stability.
  \end{itemize}
}

\cventry{Hospital Information System Intern}{Hotel Dieu De France}{Beirut}{Jun 2023 -- Aug 2023}{
  \begin{itemize}
    \item Developed SAP/Oracle SQL reports supporting clinical analytics and hospital operations.
    \item Optimized SQL queries, improving retrieval times and reporting reliability.
  \end{itemize}
}


% ------------------------------------
% RELEVANT COURSES
% ------------------------------------
% \sectionhr{Relevant Coursework}
% \begin{itemize}
%   \item \textbf{Image Processing} (Full marks) — convolution, edge detection, frequency-domain analysis, color spaces.
%   \item \textbf{Information \& Coding Theory} (Full marks) — entropy, source/channel coding, error correction.
% \end{itemize}


%------------------------------------
% PROJECTS
% ------------------------------------
\sectionhr{Technical Projects}
\projectentry{Peer-to-Peer Energy Trading System}{Energy Systems, Distributed Logic}{}{
  \begin{itemize}
    \item Contributed to the design of a peer-to-peer energy trading system modeling prosumer and consumer interactions.
    \item Developed optimization models to handle trading constraints and energy allocation.
    \item Worked within a multi-member team on system design, testing, and validation.
  \end{itemize}
}
\projectentry{AI-Aided Course Platform}{Python, SQL, LangChain, OpenAI API, React, Node.js}{}{
  \begin{itemize}
    \item Built an AI assistant enabling real-time querying of course content using LangChain and OpenAI.
    \item Designed a full-stack system integrating backend APIs, SQL storage, and a React frontend, achieving 90\%+ response relevance in peer testing.
  \end{itemize}
}
\projectentry{\href{https://github.com/eliejoefarah/Dna_PostgreSQL_Extension}{PostgreSQL DNA Sequence Extension}}{C, PostgreSQL, SP-GiST}{}{
  \begin{itemize}
    \item Developed custom DNA and k-mer data types with C-based functions for sequence processing.
    \item Designed a trie-structured SP-GiST index enabling scalable k-mer queries.
  \end{itemize}
}
\projectentry{\href{https://github.com/eliejoefarah/CompilerProjectULB}{yaLcc Compiler and LL(1) Parser}}{Java, JFlex, Compiler Design}{}{
  \begin{itemize}
    \item Implemented an LL(1) parser with grammar normalization and parsing-table generation.
    \item Integrated a JFlex scanner and produced LaTeX parse-tree visualizations for debugging.
  \end{itemize}
}

\projectentry{FPGA-Based Escape Room Game}{VHDL, Quartus II, DE2-115}{}{
  \begin{itemize}
    \item Built a two-player escape-room game using FSM-based VHDL architecture.
    \item Integrated VGA, 7-segment displays, and IR-remote input on FPGA hardware.
  \end{itemize}
}

  \projectentry{Personal Mobility Analytics \& Geospatial Visualization Platform}
{Python, GeoPandas, OSMnx, NetworkX, Scikit-learn, OpenStreetMap}{}{
  \begin{itemize}
    \item Processed large-scale Google Location History data to reconstruct time-weighted visits and movement trajectories across multiple countries.
    \item Implemented road-network map-matching using OpenStreetMap graphs and shortest-path routing to align noisy GPS traces with real infrastructure.
    \item Built spatial intensity models (KDE, hexbin) to visualize movement density, dwell behavior, and frequented vs.\ unfrequented roads.
    \item Classified visited locations by semantic purpose via nearest-POI spatial joins (amenities, transport, education, leisure).
    \item Generated high-resolution static maps and animated temporal visualizations with performance-aware rendering and subsampling.
  \end{itemize}
}

\projectentry{Personal Mobility Analytics \& Geospatial Visualization Platform}
{Python, GeoPandas, OSMnx, NetworkX, Scikit-learn, OpenStreetMap}{}{
  \begin{itemize}
    \item Processed large-scale location data to reconstruct time-weighted trajectories and behavioral patterns across regions.
    \item Built spatial models and visualizations (KDE, network mapping) to analyze movement density and semantic usage of locations.
  \end{itemize}
}



% ------------------------------------
% SKILLS
% ------------------------------------
\sectionhr{Skills}
\begin{description}

  \item[Programming Languages \& Frameworks:] 
  Java, Python, C, C++, JavaScript, Django, MATLAB

  \item[Web \& Database:] 
  SQL, PostgreSQL, REST APIs, JSON, HTML, CSS, SAP ERP

  % \item[Data \& AI:] 
  % Machine Learning, NLP, LangChain, reinforcement learning

  \item[Data \& Analytics:] 
Data Cleaning, Data Visualization, Exploratory Data Analysis, Machine Learning, Geospatial Analysis, NLP

\item[Systems \& Reliability:] 
Testing, Verification, Debugging, Requirement Analysis, Traceability
  \item[Tools:] 
  Docker, Oracle SQL Developer, Quartus, ModelSim, Jira, Qase
% \item[Hardware \& Systems:] 
%   Microprocessors, Digital Design, FPGA, VHDL, Verilog, Assembly
  \item[Languages:] 
  English, Arabic, French

\end{description}

% ------------------------------------
% VOLUNTEERING
% ------------------------------------
\sectionhr{Volunteering}

\begin{itemize}
  \item \textbf{My School Pulse}, 2018--2019 — Supported educational activities for hospitalized children.
  \item \textbf{Heartbeat – La Chaine de l’Espoir}, 2019--2020 — Assisted efforts to expand access to healthcare.
\end{itemize}

\end{document}

use resume.tex to create my website i want to make it look like  fashion website although i ama software engineer, make sure there is nit a lot o ftext